Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-23 paper.tex
Remove McMasters figure

We are looking at how Reynolds number scaling affects both the blade loading,
i.e., turbine performance, and the near-wake. Typically, static airfoil data
shows that the static stall angle increases with blade chord Reynolds number
$Re_c$ \cite{Jacobs1937}. A review of Reynolds number effects on airfoil
behavior is presented in \cite{Lissaman1983}. In general, airfoil performance is
enhanced as the boundary layer on the foil transitions to turbulence closer to
the leading edge, which enables it to advance further downstream against the
adverse pressure gradient on the suction side, delaying separation to higher
angles of attack. For smooth airfoils, this transition can cause a dramatic
increase in foil performance, at a blade chord Reynolds number on the order of
$10^5$ \cite{McMasters1980}, shown in Figure~\ref{fig:McMasters}. Note that
there is a distinct lack of highly reliable data for airfoils in this
transitional regime and below. An evaluation of the various databases relevant
to cross-flow turbines is presented in \cite{Bedon2014}.

\includegraphics[width=0.7\textwidth]{figures/McMasters-Henderson-1980}

\caption{Airfoil maximum lift-to-drag ratio versus Reynolds number, from
    \cite{McMasters1980}.}

\label{fig:McMasters}
\end{figure}

>>>>

We are looking at how Reynolds number scaling affects both the blade loading,
i.e., turbine performance, and the near-wake. Typically, static airfoil data
shows that the static stall angle increases with blade chord Reynolds number
$Re_c$ \cite{Jacobs1937}. A review of Reynolds number effects on airfoil
behavior is presented in \cite{Lissaman1983}. In general, airfoil
performance---often characterized by the profile's lift-to-drag ratio---is
enhanced as the boundary layer on the foil transitions to turbulence closer to
the leading edge, which enables it to advance further downstream against the
adverse pressure gradient on the suction side, delaying separation to higher
angles of attack. For smooth airfoils, this transition can cause a dramatic
increase in foil performance at a blade chord Reynolds number on the order of
$10^5$ \cite{McMasters1980}. Note that there is a distinct lack of highly
reliable data for airfoils in this transitional regime and below. An evaluation
of the various databases relevant to cross-flow turbines is presented in
\cite{Bedon2014}.
